\bf Patent Duration, Innovative Performance, and Technology Diffusion

### 2021-01-08 paper/paper.tex
modify style to match conference requirements

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Journal Article
% LaTeX Template
% Version 1.4 (15/5/16)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Frits Wenneker (http://www.howtotex.com) with extensive modifications by
% Vel (vel@LaTeXTemplates.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[twoside,twocolumn]{article}

\usepackage{blindtext} % Package to generate dummy text throughout this template

\usepackage[sc]{mathpazo} % Use the Palatino font
\usepackage[T1]{fontenc} % Use 8-bit encoding that has 256 glyphs
\linespread{1.05} % Line spacing - Palatino needs more space between lines
\usepackage{microtype} % Slightly tweak font spacing for aesthetics

\usepackage[english]{babel} % Language hyphenation and typographical rules

\usepackage[hmarginratio=1:1,top=32mm,columnsep=20pt]{geometry} % Document margins
\usepackage[hang, small,labelfont=bf,up,textfont=it,up]{caption} % Custom captions under/above floats in tables or figures
\usepackage{booktabs} % Horizontal rules in tables

\usepackage{lettrine} % The lettrine is the first enlarged letter at the beginning of the text

\usepackage{enumitem} % Customized lists
\setlist[itemize]{noitemsep} % Make itemize lists more compact

\usepackage{abstract} % Allows abstract customization
\renewcommand{\abstractnamefont}{\normalfont\bfseries} % Set the "Abstract" text to bold
\renewcommand{\abstracttextfont}{\normalfont\small} % Set the abstract itself to small italic text

\usepackage{titlesec} % Allows customization of titles
\renewcommand\thesection{\Roman{section}} % Roman numerals for the sections
\renewcommand\thesubsection{\Roman{subsection}} % roman numerals for subsections
\titleformat{\section}[block]{\large\scshape\centering}{\thesection.}{1em}{} % Change the look of the section titles
\titleformat{\subsection}[block]{\large}{\thesubsection.}{1em}{} % Change the look of the section titles

\usepackage{fancyhdr} % Headers and footers
\pagestyle{fancy} % All pages have headers and footers
\fancyhead{} % Blank out the default header
\fancyfoot{} % Blank out the default footer
\fancyhead[C]{Running title $\bullet$ May 2016 $\bullet$ Vol. XXI, No. 1} % Custom header text
\fancyfoot[RO,LE]{\thepage} % Custom footer text

\usepackage{titling} % Customizing the title section

\usepackage{hyperref} % For hyperlinks in the PDF

%----------------------------------------------------------------------------------------
%	TITLE SECTION
%----------------------------------------------------------------------------------------

\setlength{\droptitle}{-4\baselineskip} % Move the title up

\pretitle{\begin{center}\Huge\bfseries} % Article title formatting
\posttitle{\end{center}} % Article title closing formatting
\title{ISODS: An ISODATA-Based Initial Centroid Algorithm} % Article title
\author{%
  \textsc{
    Noah Gardner$^1$\thanks{ngardn10@students.kennesaw.edu}, 
    Sahar Yarmohammadtoosky$^2$\thanks{yarmohamadishr@gmail.com},
    }\\[1ex]
  \textsc{
    Anthony Phan$^1$\thanks{aphan5@students.kennesaw.edu},
    Chih-Cheng Hung$^1$\thanks{chung1@students.kennesaw.edu}} \\[1ex]
  \normalsize $^1$Kennesaw State University \\
  \normalsize College of Computing and Software Engineering \\
  \normalsize Marietta, GA, USA \\[1ex]
  \normalsize $^2$Iran University of Science and Technology \\
  \normalsize Tehran, Iran
}
\date{} % Leave empty to omit a date

\renewcommand{\maketitlehookd}{%
\begin{abstract}
\noindent 
Iterative Self-Organizing Data Analysis Technique (ISODATA) is a clustering
algorithm based on K-Means that intends to find the correct number of clusters
through merging and splitting. Compared to K-Means, the ISODATA algorithm should
be resilient to initial cluster centers. However, ISODATA is also sensitive to
initial cluster centers which impacts the performance of the algorithm. This
work proposes using the ISODATA approach of splitting clusters to select quality
initial cluster centers. The proposed approach is evaluated on several benchmark
UCI datasets as well as the Salinas-A hyperspectral image dataset. The results
are evaluated using standard clustering evaluation parameters. \\ \\
\textit{\textbf{Keywords:} Clustering, ISODATA, Initial Centroid, Remote Sensing} \\
\end{abstract}
}

%----------------------------------------------------------------------------------------

\begin{document}

% Print the title
\maketitle

%----------------------------------------------------------------------------------------
%	ARTICLE CONTENTS
%----------------------------------------------------------------------------------------

@@

\lettrine[nindent=0em,lines=3]{R} emote sensing technology is used when the data
collection takes place at a remote distance from the subject matter, such as the
study of daily weather and long-term climate change, land cover monitoring,
ecosystem modeling of vegetation, and so on \cite{Jensen1996,Mallapragada2018}.
Multispectral imaging technology is one of the instruments for remote sensing
used since the late 1960s \cite{Khan2018,Landgrebe1999}. However, multispectral
imaging systems use a low number of spectral bands (three to six spectral bands
in different systems). Increasing spectral resolution in the hyperspectral
images (HSI) with several hundred spectral bands of the observational scene in a
single acquisition makes it possible to acquire detailed examination of
observational scenes \cite{Khan2018}. The ground-based version of hyperspectral
images has gained immense interest. It has been applied to numerous electronic
imaging applications, including food inspection, forensic science, medical
surgery and diagnosis, and military applications
\cite{Govender2009,Adam2009,Fischer2006,Carrasco2003}. Because of the difficulty
of obtaining prior knowledge in remote sensing studies, unsupervised
classification and cluster analysis have great importance compared to supervised
classification \cite{Abbas2016}.

@@

% The paper is organized as follows: Section 2 introduces K-Means and ISODATA
% clustering algorithms. The new proposed algorithm is explained in Section 3. We
% present the experimental results in Section 4. Finally, Section 5 contains
% concluding remarks.

%------------------------------------------------

@@

%------------------------------------------------

@@

%------------------------------------------------

@@

%------------------------------------------------
\section{Results}

@@

For experiments 1 and 2, we explore applying ISODS to ISODATA and K-Means by
using benchmark UCI datasets Iris, Wine, and Glass. We also show results from
applying Random Centers and K-Means++ Centers. To evaluate the cluster results,
external cluster validation measures are used. We utilize pair-counting measures
which rely on counting matching pairs between two sets of data to determine
agreement and disagreement \cite{Rezaei2016}. The pair-counting measures applied
are \textit{rand index} (RI - agreement probability), \textit{adjusted rand
  index} (ARI), \textit{mirkin's index} (MI - disagreement probability), and
\textit{hubert's index} (HI - $P(agree) - P(disagree)$)\cite{Hubert1985}
\cite{Meila2003}.

%------------------------------------------------

\section{Conclusion}

\subsection{Subsection One}

\blindtext % Dummy text

\subsection{Subsection Two}

\blindtext % Dummy text

%----------------------------------------------------------------------------------------
%	REFERENCE LIST
%----------------------------------------------------------------------------------------

@@

%----------------------------------------------------------------------------------------

>>>>

\documentclass[a4paper,10pt]{article}
\usepackage{graphicx}
\begin{document}

\title{\bf Patent Duration, Innovative Performance, and Technology Diffusion}
\author{Noah Gardner$^1$,
      Sahar Yarmohammadtoosky$^2$, \\
      Anthony Phan$^3$,
      and Chih-Cheng Hung$^4$\\[1ex]
      \sl \small Kennesaw State University,
      Marietta, GA, USA$^{1, 3, 4}$\\
      \sl \small Iran University of Science and Technology,
      Tehran, Iran$^2$\\[1ex]
      \small $^1$ngardn10@students.kennesaw.edu, 
      \small $^2$yarmohamadishr@gmail.com, \\
      \small $^3$aphan5@students.kennesaw.edu,
      \small $^4$chung1@kennesaw.edu, \\}
\date{}
\maketitle

\begin{abstract}
      \noindent 
      Iterative Self-Organizing Data Analysis Technique (ISODATA) is a clustering
      algorithm based on K-Means that intends to find the correct number of
      clusters through merging and splitting. Compared to K-Means, the ISODATA
      algorithm should be resilient to initial cluster centers. However, ISODATA
      is also sensitive to initial cluster centers which impacts the performance
      of the algorithm. This work proposes using the ISODATA approach of splitting
      clusters to select quality initial cluster centers. The proposed approach is
      evaluated on several benchmark UCI datasets as well as the Salinas-A
      hyperspectral image dataset. The results are evaluated using standard
      clustering evaluation parameters. \\
      {\bf Keywords :} Clustering, ISODATA, Initial Centroid, Remote Sensing
\end{abstract}

% =========================================================================== %

@@

Remote sensing technology is used when the data collection takes place at a
remote distance from the subject matter, such as the study of daily weather and
long-term climate change, land cover monitoring, ecosystem modeling of
vegetation, and so on \cite{Jensen1996,Mallapragada2018}. Multispectral imaging
technology is one of the instruments for remote sensing used since the late
1960s \cite{Khan2018,Landgrebe1999}. However, multispectral imaging systems use
a low number of spectral bands (three to six spectral bands in different
systems). Increasing spectral resolution in the hyperspectral images (HSI) with
several hundred spectral bands of the observational scene in a single
acquisition makes it possible to acquire detailed examination of observational
scenes \cite{Khan2018}. The ground-based version of hyperspectral images has
gained immense interest. It has been applied to numerous electronic imaging
applications, including food inspection, forensic science, medical surgery and
diagnosis, and military applications
\cite{Govender2009,Adam2009,Fischer2006,Carrasco2003}. Because of the difficulty
of obtaining prior knowledge in remote sensing studies, unsupervised
classification and cluster analysis have great importance compared to supervised
classification \cite{Abbas2016}.

@@

The paper is organized as follows: Section 2 introduces K-Means and ISODATA
clustering algorithms. The new proposed algorithm is explained in Section 3. We
present the experimental results in Section 4. Finally, Section 5 contains
concluding remarks.

% =========================================================================== %

\section{Background}

@@

@@

% =========================================================================== %

@@

% =========================================================================== %

\section{Results}

@@

For experiments 1 and 2, we explore applying ISODS to ISODATA and K-Means by
using benchmark UCI datasets Iris, Wine, and Glass. We also show results from
applying Random Centers and K-Means++ Centers. To evaluate the cluster results,
external cluster validation measures are used. We utilize pair-counting measures
which rely on counting matching pairs between two sets of data to determine
agreement and disagreement \cite{Rezaei2016}. The pair-counting measures applied
are \textit{rand index} (RI - agreement probability), \textit{adjusted rand
      index} (ARI), \textit{mirkin's index} (MI - disagreement probability), and
\textit{hubert's index} (HI - $P(agree) - P(disagree)$)\cite{Hubert1985,
      Meila2003}.

% =========================================================================== %

\section{Conclusion}
Put Conclusion here.

% =========================================================================== %

\subsection*{Acknowledgements}
Put Acknowledgements here.

\vspace{5mm}

\begin{center}
      {\large \bf References}
\end{center}

@@
